Tables & figures for paper reporting increase of home deaths 2020

### 2021-05-05 paper_reporting_death_at_home_increase.Rmd
added figure and table 3 - age group breakdowns

@@

>>>>

## Table of deaths by age

```{r}
table_3_paper <-
  total_deaths_age %>%
  filter(str_starts(place_of_death, "Home") & year == 2020) %>%
  filter(!age %in% c("0","1-14")) %>%
  mutate(deaths_non_covid_2020 = deaths_all_causes - deaths_covid_related) %>%
  mutate(
    `Percent increase (All home deaths)` = scales::percent(ratio_annual_deaths_to_historical_mean - 1, accuracy = 0.1)
    ) %>%
  select(`Age` = age, `All Deaths (Home)` = deaths_all_causes, `Non-covid deaths (Home)` = deaths_non_covid_2020, `Percent increase (All home deaths)`)

write.xlsx(x = table_3_paper, file = paste0(dir_paper, "/percent_increase_by_age.xlsx"))
```

@@

## Grayscale plot of weekly deaths by age, 2020

```{r}
(figure3 <-
  merged_deaths_age %>%
  filter(year == 2020) %>%
  filter(!age %in% c("0","1-14")) %>%  # remove youngest age groups
  # filter(!place_of_death %in% c("All","Other")) %>%
  filter(str_starts(place_of_death,"Home")) %>%
  # mutate(place_of_death = factor(place_of_death, levels = c("Hospital", "Home & other non-institution", "Care home"))) %>%  # needs to be factor with same levels, otherwise it messes up level order when added as geom_text later!)
  mutate(fill_text = "Historical range") %>%  # added for ease of using aes(fill) later
  pivot_longer(cols = c(deaths_all_causes, deaths_non_covid, deaths_mean), 
               names_to = "deaths_type", values_to = "deaths") %>%
  mutate(deaths_type = factor(x = deaths_type, levels = c("deaths_all_causes", "deaths_non_covid", "deaths_mean"), labels = c("All deaths", "Non Covid-19 deaths", "Historical mean"))) %>%
  ggplot(aes(x = week_number_run_over)) +
  geom_ribbon(aes(ymin = deaths_min, ymax = deaths_max, fill = fill_text), alpha = 0.5) +
  geom_line(aes(y = deaths, linetype = deaths_type, colour = deaths_type)) +
  scale_colour_manual(values = c("black", "black", "gray30")) +
  scale_x_continuous(breaks = seq(0,60,by=10)) +
  ylim(0, NA) +  # start scale at 0 for better understanding the scale of deaths
  facet_wrap(~age) +
  scale_fill_manual(values = c("grey70")) +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    legend.box.spacing = unit(0, "cm"),
    plot.caption = element_text(size = 10, colour = "gray60")
    ) +
  labs(x = "Week number",
       y = "Deaths (N)",
       caption = paste0(c(death_registrations_text, source_nrs_text), collapse="\n")
       ) +
  NULL
)
## figure for a bit less than half A4 page is approx 14*11cm
save_output_file(filename = paste0(dir_paper,"/figure3"), extensions = c(".pdf",".svg",".png",".tiff"), plot = figure3, width = 28, height = 11, units = "cm", dpi = 300)

save_output_file(filename = paste0(dir_paper,"/figure3_hires"), extensions = c(".png"), plot = figure3, width = 28, height = 11, dpi = 1200, units = "cm")
```
